Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-14 manuscript.tex
THC figures

\funding{
This research was funded by the European Union ERA-NET CHIST-ERA 2018 research and innovation program under grant number ANR-19-CHR3-0008-03 (``\href{APROVIS3D}{http://aprovis3d.eu/}''). % Agence Nationale de la Recherche %HL and 
LP, CB and AG received funding from the ANR grant number ANR-20-CE23-0021 ``\href{AgileNeuroBot}{https://laurentperrinet.github.io/grant/anr-anr/}''
% LP received funding 
and LP from A*Midex grant number AMX-21-RID-025
``\href{PolyChronies}{https://laurentperrinet.github.io/grant/polychronies/}''.}

>>>>

\funding{
This research was funded by the European Union ERA-NET CHIST-ERA 2018 research and innovation program under grant number ANR-19-CHR3-0008-03 (``\href{http://aprovis3d.eu/}{APROVIS3D}''). % Agence Nationale de la Recherche %HL and 
LP, CB and AG received funding from the ANR grant number ANR-20-CE23-0021 ``\href{https://laurentperrinet.github.io/grant/anr-anr/}{AgileNeuroBot}''
% LP received funding 
and LP from A*Midex grant number AMX-21-RID-025
``\href{https://laurentperrinet.github.io/grant/polychronies/}{Polychronies}''.}
